% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass{deedy-resume-openfont}
\usepackage{fancyhdr}
 \usepackage{fontawesome}
 \usepackage{ragged2e}
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Aditi Goyal}{ \urlstyle{same}\href{}{Junior Year  }|\href{}{ Electrical Engineering  }| \href{}{IIT Jodhpur}\\
\href{mailto:goyal.16@iitj.ac.in}{goyal.16@iitj.ac.in} | (+91) 7045330834}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\vspace{1mm}
\subsection{IIT JODHPUR}
\descript{Btech in Electrical Engineering}
\descript{Department Rank - 2}
\location{Expected 2023}
\location{ Cum. GPA: 8.79 / 10} (uptil 4th Semester)
\sectionsep

\subsection{Vidya Niketan J.College}
\descript{Class 12 | HSC}
\location{2019 | Mumbai,India}
\descript{Percentage: 89.54\%}
\sectionsep

\subsection{Vissanji Academy}
\descript{Class 10 | ICSE}
\location{ 2017 | Mumbai. India}
\descript{Percentage: 96.8\%(agg.)}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\subsection{Languages}

\textbullet{}C /C++\textbullet{} Python \textbullet{} HTML/CSS \\\textbullet{} Dart \textbullet{} Verilog \textbullet{}Javascript\\
\location{Machine Learning:}
\textbullet{} sklearn\textbullet{}pytorch\textbullet{}Tensorflow\\
\sectionsep
\subsection{Development}
 \textbullet{}Bootstrap \textbullet{}Django\\
 \textbullet{}Flutter \textbullet{}Firebase
 \textbullet{}Git\\\textbullet{} GraphQL\textbullet{}AdobeXD\\
\sectionsep
\subsection{Others}
 \textbullet{}Competitive Programming \\\textbullet{}Photoshop\textbullet{} SolidWorks\\
 \textbullet{}Debating\textbullet{}Public Speaking\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/gaditi123}{\bf gaditi123 }\href{https://github.com/gaditi123}{\faExternalLink} \\
LinkedIn://  \href{https://www.linkedin.com/in/aditi-goyal-21b834196/}{\bf Aditi Goyal }\href{https://www.linkedin.com/in/aditi-goyal-21b834196/}{\faExternalLink} \\
%Codeforces://  \href{https://codeforces.com/profile/DuhAditi}{\bf DuhAditi} \\
Codechef://  \href{https://www.codechef.com/users/duhaditi}{\bf duhaditi }\href{https://www.codechef.com/users/duhaditi}{\faExternalLink} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
Probability, Statistics and Stoch. Process \\
Linear Algebra and Calculus \\
Intro to Computer Science \\
Data Structures and Algorithm\\
Pattern Recognition and Machine Learning\\
Intro to Quantum Information\\

\sectionsep

\subsection{MOOC}
Responsive Web Development\\
Django \\
Dart and Flutter \\
\sectionsep 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\vspace{1mm}
\runsubsection{StopStalk App}
\descript{| Flutter Developer}
\location{October 2020 – April 2021 | Flutter, Firebase | Github \href{https://github.com/devlup-labs/stopstalk-android}{\faExternalLink} |  \textbf{Playstore \href{https://play.google.com/store/apps/details?id=com.Stopstalk.android}{\faExternalLink}}}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
{\justifying
\item Collaborated with popular open source project StopStalk in a team of 4 to build a versatile mobile app with a minimalist and intuitive UI/UX.
\item \textbf{Executed core functionalities} like: graphs, form-based components, animated lists, login along with \textbf{search and sort} features reaching 150+ users in 3 days.
\item Implemented real time JSON updates,\textbf{ dynamic updates} like add/delete friends or ToDo, reusable components and was the \textbf{top contributor} in the project.
\par}
\end{tightemize}
\sectionsep

\sectionsep
\section{Projects}
\vspace{1mm}
\runsubsection{Lokalite}
\descript{| Junior Flutter Developer}
\location{May 2020 – June 2020 |\textbf{ Flutter, Django }| \href{https://gitlab.com/lokalite/app}{Gitlab }\href{https://gitlab.com/lokalite/app}{\bf \faExternalLink} }
\begin{tightemize}
{\justifying
\item Developed a comprehensive restaurant listing app with \textbf{geolocation based restaurant discovery} service and social features like chatting and search.
\item Contributed functionalities like: submitting reviews and images, user profile, connecting to google maps and separate user and merchant interface UI/UX.
\par}
\end{tightemize}
\sectionsep

\runsubsection{Souvenirs IITJ 
\href{https://devlup-labs.github.io/souvenirs_iitj/}}{\bf \faExternalLink}
\descript{| Design and Arts Society ,IIT Jodhpur website }
\location{April 2020 - May 2020 |\textbf{ Bootstrap, Javascript, GoogleAppScripts } | \href{https://github.com/devlup-labs/souvenirs_iitj}Github \href{https://github.com/devlup-labs/souvenirs_iitj}{\bf \faExternalLink}}
\begin{tightemize}
{\justifying

\item Portal to publicly display photos of events held in the institute \textbf{without any dedicated server space}, completely based on using google drive for storage purposes.

\item Devised a logic to \textbf{automate image URLs} without hard-coding any, using \textbf{GAS functionalities} and improved the overall front end in a team of 4.

\par}
\end{tightemize}
\sectionsep

\runsubsection{Pattern Recognition and Machine Learning}
\location{}
\begin{tightemize}
{\justifying
\item Worked extensively on all ML classifiers like regression, decision tress, boosting, clustering and deep neural networks using Pytorch and Tensorflow.

\item Designed and developed a \textbf{drug review sentiment analysis NLP} project with classifier combination of ML classifiers and deep neural networks, performing \textbf{feature engineering, predictive analysis} and simulation development.\href{https://github.com/harsh-ux/Sentiment-Analysis-of-Drug-Reviews}{\textbf{Github }}\href{https://github.com/harsh-ux/Sentiment-Analysis-of-Drug-Reviews}{\faExternalLink}

\item Improved \textbf{face mask detection} using several optimised CNN models. \href{https://github.com/gaditi123/mask_detection}{\textbf{Github }}\href{https://github.com/gaditi123/mask_detection}{\faExternalLink}

\par}
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements} 
\begin{tabular}{rll}

2020        & \textbf{Department Rank 2} of Electrical Branch till 4th semester\\
2020 		 & \textbf{Research paper} documenting Covid-19's impact on WASH and secured\\
 &\textbf{ $2^{nd}$ place} with \textbf{cash prize} in an institute challenge. \href{https://iitj.ac.in/uploaded_docs/summer\%20challenge_revised_03112020.pdf}{\bf \faExternalLink}\\
2019	     & \textbf{JEE 2019} - Top 0.8 percentile of 1.3 million candidates\\
2019	     & Top 1\% of Maharashtra State Board Class 12  Exam\\
\end{tabular}
\sectionsep

\section{Position of Responsibility} 
\begin{tabular}{rll}
2020 		 & Literature Society |\custombold \textbf{ JOINT SECRETARY}\\
2020        & Core Member: \href{https://github.com/devlup-labs}{\bf \textbf{Devlup Labs}: OpenSource Dev Group}\\

\end{tabular}
\sectionsep

\section{Extracurricular} 
\vspace{\topsep}
\begin{tightemize}
{\justifying
\item \textbf{Parliamentary Debate} at the InterIIT Cultural Meet, IIT Bombay, December'19.
\item Received\textbf{ Best Delegate Award} in India-International MUN Conference.
\item \textbf{Hosted} opening ceremony of Spandan(Inter Hostel Fest) and Kavi Samelan of renowned Jodhpur poets besides managing several club activities.

\par}
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
