%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Aditi Goyal (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass{deedy-resume-openfont}
\usepackage{fancyhdr}
 \usepackage{fontawesome}
 \usepackage{ragged2e}
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{Aditi Goyal}{ \urlstyle{same}\href{}{Sophomore Year  }|\href{}{ Electrical Engineering  }| \href{}{IIT Jodhpur}\\
\href{mailto:goyal.16@iitj.ac.in}{goyal.16@iitj.ac.in} | (+91) 7045330834}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\vspace{1mm}
\subsection{IIT JODHPUR}
\descript{Btech in Electrical Engineering}
\descript{Department Rank - 3}
\location{Expected 2023}
\location{ Cum. GPA: 8.64 / 10}
\sectionsep

\subsection{Vidya Niketan J.College}
\descript{Class 12 | HSC}
\location{2019 | Mumbai,India}
\descript{Percentage: 89.54\(\%}
\sectionsep

\subsection{Vissanji Academy}
\descript{Class 10 | ICSE}
\location{ 2017 | Mumbai. India}
\descript{Percentage: 96.8\(\%(agg.)}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
\faGithub\hspace{1mm} Github:// \href{https://github.com/gaditi123}{\bf gaditi123} \\
\faLinkedin\hspace{1mm} LinkedIn://  \href{https://www.linkedin.com/in/aditi-goyal-21b834196/}{\bf Aditi Goyal} \\
%Codeforces://  \href{https://codeforces.com/profile/DuhAditi}{\bf DuhAditi} \\
Codechef://  \href{https://www.codechef.com/users/duhaditi}{\bf duhaditi} \\
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\subsection{Languages}
\location{Proficient:}
\textbullet{}C /C++\textbullet{} Python \textbullet{} HTML/CSS \\\textbullet{} Dart \textbullet{} Verilog \\
\location{Familiar:}
\textbullet{}Javascript\textbullet{} MATLAB \textbullet{}LaTeX\\
\sectionsep
\subsection{Development}
 \textbullet{}Bootstrap \textbullet{}Django\\
 \textbullet{}Flutter \textbullet{}Firebase
 \textbullet{}Git\\\textbullet{} GraphQL\\
\sectionsep
\subsection{Others}
 \textbullet{}Competitive Programming \\\textbullet{}Photoshop\textbullet{} SolidWorks\textbullet{}Public Speaking\textbullet{}Debating\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
Probability, Statistics and Stochastic Process \\
Linear Algebra and Calculus \\
Intro to Computer Science \\
Data Structures and Algorithm\\
Pattern Recognition and Machine Learning\\
Intro to Quantum Information\\

\sectionsep

\subsection{MOOC}
Responsive Web Development\\
Django \\
Dart and Flutter \\
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\vspace{1mm}
\runsubsection{StopStalk App}
\descript{| Flutter Developer}
\location{September 2020 – Present | Github \href{https://github.com/devlup-labs/stopstalk-android}{\faExternalLink} |  \textbf{Flutter, Firebase}}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
{\justifying
\item Collaborating with popular open source project StopStalk in a team of 5 to build a versatile mobile application with a minimalist and intuitive UI/UX. 
\item Executed core functionalities like: graphs,calendar reminder notification ,animated lists, login along with search and sort features. 
\item Implemented real time JSON data updates, dynamic updates like add friends or todo and was the top contributor in the project.
\par}
\end{tightemize}
\sectionsep

\sectionsep
\section{Projects}
\vspace{1mm}
\runsubsection{Lokalite}
\descript{| Junior Flutter Developer}
\location{May 2020 – June 2020 | Gitlab \href{https://gitlab.com/lokalite/app}{\bf \faExternalLink} | \textbf{Flutter, Django}}
\begin{tightemize}
{\justifying
\item Developed a comprehensive restaurant listing app with geolocation based restaurant discovery service and social features like chatting and search.
\item Contributed functionalities like: submitting reviews and images, connecting to google maps and separate user and merchant interface UI/UX.
\par}
\end{tightemize}
\sectionsep

\runsubsection{Souvenirs IITJ 
\href{https://devlup-labs.github.io/souvenirs_iitj/}}{\bf \faExternalLink}}
\descript{| Design and Arts Society ,IIT Jodhpur website }
\location{April 2020 - May 2020 | Github \href{https://github.com/devlup-labs/souvenirs_iitj}{\bf \faExternalLink} | \textbf{ Bootstrap, Javascript, GoogleAppScripts}}
\begin{tightemize}
{\justifying
\item Portal to publicly display photos of events held in the institute without any dedicated server space, completely based on using google drive for storage purposes.
\item Developed a logic to automate image URLs without hard-coding any using GAS functionalities and assisted in the overall front end in a team of 4.
\par}
\end{tightemize}
\sectionsep

\runsubsection{Bio-plastics from Banana Peels}
\descript{| Engineering Design}
\location{September 2019 –  March 2020}
\begin{tightemize}
{\justifying
\item Headed a team of 10 for a research project for 2 semesters range and working tirelessly to explore and asses use cases , techniques and best materials to use to make plastic out of ordinary banana peels. 
\item Engineered a prototype from institute financing with results to support our claims and came in top 6 amongst 40+ competing teams.

\par}
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards and Positions of Responsibility} 
\begin{tabular}{rll}
2020 		 & Literature Society |\custombold \textbf{ JOINT SECRETARY}\\
2020 		 & Coauthored a \textbf{research paper} documenting Covid-19's impact on water,\\
				& sanitation and hygiene and in India and secured\textbf{ $2^{nd}$ place} with \textbf{cash prize} in \\
                &institute wide competition. \href{https://iitj.ac.in/uploaded_docs/summer\%20challenge_revised_03112020.pdf}{\bf \faExternalLink}\\
2019	     & Top 0.8 percentile students in JEE Advanced | 2019\\
2019	     & Top 1\% of Maharashtra State Board Class 12  Exam\\
\end{tabular}
\sectionsep

\section{Extracurricular} 
\location{Other notable aspects:}
\begin{tightemize}
{\justifying
\item Core Member: \href{https://github.com/devlup-labs}{\bf \textbf{Devlup Labs}: OpenSource Dev Group}.
\item Participated in \textbf{Parliamentary Debate} at the InterIIT Cultural Meet, IIT Bombay, December'19.
\item Received\textbf{ Best Delegate Award} in India-International MUN Conference.
\item \textbf{Hosted} opening ceremony of Spandan(Inter Hostel Fest) and Kavi Samelan of renowned Jodhpur poets .

\par}
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
